Precise predictions for same-sign W-boson scattering at the LHC

### 2018-06-12 Draft_EPJC/Referee/answer_referee.tex

\begin{center}
  \LARGE \textbf{Author answer to the referee report of EPJC-18-04-021}
\end{center}
\vspace{0.5cm}
We thank the referee for the positive report and for her/his insightful comments and detailed comments. Below, we address all the questions and suggestions contained in the report in order. To ease the reading, the points raised by the referee (quoted in italic) are followed by an  explanation of the actions undertaken to address them.

\vspace{0.5cm}
\begin{enumerate}

    \item \emph{At the beginning of Sec. 2 "LO" is defined as the three possible coupling
combinationas $\alpha^6$, $\alpha_s \alpha^5$, $\alpha_s^2 \alpha^4$. However for most of the paper "LO" is more 
and more taken equivalent to only mean the EW $\alpha^6$ contribution. (At first it still says "LO at $\alpha^6$", 
then it becomes
LO i.e. $\alpha^6$, and eventually in the LO+PS section the coupling order is dropped completely. 
This is of course just semantics, but it was quite confusing on the first reading and it would be good to make this a bit clearer from the start.}

In section 2, before the last paragraph, we have added the following sentence:
\begin{quote}
In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.  
\end{quote}
For clarity, we have also re-stated the coupling orders at the beginning of section 6 (Matching to parton shower).

@@

\item \emph{ page 18, 2nd column, line 48: "on the other ..." the part of the sentence is
    nonsensical.}

We have corrected the sentence.
\begin{quote}
which clearly suggest not to rely on a single tool/parton shower, and on the other make\ldots
\end{quote}
to
\begin{quote}
which on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make\ldots
\end{quote}

\item \emph{page 19, 1st column, line 14:
I think it is important to not mistake "more realistic" for "conservative". The
scale variations are clearly underestimating the actual theoretical uncertainties. This does not mean that another method, which implies larger uncertainties, is "conservative", it is simply (hopefully) "more realistic". Conservative is easily (mis)interpreted as possibly overestimated, which I don't think is the case here. (In fact, there is no guarantee that even the comparison of different tools will provide an estimate that covers the next order, so calling this a conservative estimate is really misplaced.}

We have replaced ``conservative'' with ``more realistic'', as suggested.

\item We have modified the sentence:
``combined measurements which are better theoretically defined'' to ``combined measurements which are theoretically better defined''.

\item We have updated the LO+PS plots.
It has been found that the predictions for WHIZARD+P8 suffered from a bug which has now been fixed.
The agreement with other Pythia parton-shower predictions is now even better.
In addition, the plot at LO+PS for the Zeppenfeld variable of the third jet suffered from a miss-match of the PHANTOM+H7-default due to bug in the plotting routine.
Again, the predictions of Phantom+H7-default are now in better agreement with Herwig parton-shower predictions is improved.
No modifications to the text have been made.

### 2018-06-12 Draft_EPJC/article.tex
Modification of the article and referee answer

In the rest of this paper, the notation ``LO'' or ``NLO(-QCD)'' without any specification of coupling powers will refer to the contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ respectively.

In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
These cuts are based on the different kinematical behaviour of the contributions.
The EW contribution is characterised by two jets with large rapidities as well as a large di-jet invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
defined.
Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.\\

@@

\section{Matching to parton shower}
    \label{sec:matching}
We now discuss how different predictions compare when the matching to parton shower is included, both at LO 
($\mathcal O (\alpha^6)$) and at NLO-QCD ($\mathcal O (\alpha^6\alphas)$) accuracy. For such
a comparison we expect larger discrepancies than what we found at fixed order, as a consequence of the different
matching schemes, parton showers employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
restrict ourselves to show results only in the VBS approximation,
{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
{\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower is employed. 
The same parton showers are employed for the LO results of {\sc PHANTOM}.
{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houches Accord
interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
matching. As parton show\-er, both the default angular-ordered shower as
well as the dipole shower can be employed. We use here the subtractive (MC@NLO-type) matching to these parton-show\-er algorithms.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.

>>>>

In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.

In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
These cuts are based on the different kinematical behaviour of the contributions.
The EW contribution is characterised by two jets with large rapidities as well as a large di-jet invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
defined.
Hence, combined measurements which are theoretically better defined should be preferably performed by the experimental collaborations at the LHC.

@@

\section{Matching to parton shower}
    \label{sec:matching}
We now discuss how different predictions compare when the matching to parton shower is included, both at LO 
(\emph{i.e.}\ at order $\mathcal O (\alpha^6)$) and at NLO-QCD (\emph{i.e.}\ at order $\mathcal O (\alpha^6\alphas)$) accuracy. For such
a comparison we expect larger discrepancies than what we found at fixed order, as a consequence of the different
matching schemes, parton showers employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
restrict ourselves to show results only in the VBS approximation,
{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
{\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower is employed. 
The same parton showers are employed for the LO results of {\sc PHANTOM}.
{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houches Accord
interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
matching. As parton show\-er, both the default angular-ordered shower as
well as the dipole shower can be employed. We use here the subtractive (MC@NLO-type) matching to these parton-show\-er algorithms.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
